Constraining gravitational wave amplitude birefringence with GWTC-3

### 2023-04-07 src/tex/ms.tex
fill Fig 5
fig 5

\begin{figure}
    \script{posterior_kappa.py}
    \includegraphics[width=\columnwidth]{figures/posterior_kappa.pdf}
    \caption{
        The generic and restricted posterior of $\kappa$.
        The blue solid and dashed lines show the restricted posterior of $\kappa$ with and without GW200129, respectively.
        The orange solid and dashed lines show the generic posterior of $\kappa$ with and without GW200129, respectively.
        The black dashed line marks the absence of birefringence ($\kappa=0$).
    }
    \label{fig:posterior_kappa}
\end{figure}

>>>>

\begin{figure}
    \script{posterior_kappa.py}
    \includegraphics[width=\columnwidth]{figures/posterior_kappa.pdf}
    \caption{
        Restricted and generic posteriors on $\kappa$, which respectively do and do not assume that $\kappa$ is shared by all events (color).
        Solid and dashed traces indicate whether the analysis included GW200129 or not.
        The black dashed line marks the absence of birefringence ($\kappa=0$).
        The shaded distribution is the primary result in this work (blue band in Fig.~\ref{fig:violin_kappa}).
    }
    \label{fig:posterior_kappa}
\end{figure}
